\documentclass[letterpaper, 10pt]{article}

\usepackage{graphicx} % Required for inserting images
\usepackage[hidelinks]{hyperref} % Required for hyperlinks
\usepackage[top=0.5in, bottom=0.5in, left=0.7in, right=0.7in]{geometry} % Page margins

\pagestyle{empty} % No page numbers

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\LARGE Kim Inchan} \\ \vspace{2pt}
    \href{mailto:iamkic12@gmail.com}{\underline{iamkic12@gmail.com}} $|$
    \href{https://github.com/iamkic12-netizen}{\underline{github.com/iamkic12-netizen}}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section*{Technical Skills}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[] \textbf{Programming}: Python, C, C++, Java, JavaScript
    \item[] \textbf{Frameworks \& Tools}: Git, GitHub, React, Node.js, VS Code, Linux
    \item[] \textbf{Languages}: Korean (Native), English (Intermediate)
\end{itemize}

%-----------EXPERIENCE-----------
\section*{Experience}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[]
    \textbf{Software Engineering Intern} \hfill Jun. 2024 -- Aug. 2024 \\
    \textit{Kakao Corp.} \hfill \textit{Seongnam, Korea}
    \begin{itemize}
        \item Contributed to backend API development using Spring Boot and MySQL.
        \item Wrote unit tests and improved code coverage by 15\% for the notification service.
    \end{itemize}
    \item[]
    \textbf{Undergraduate Teaching Assistant} \hfill Mar. 2024 -- Jun. 2024 \\
    \textit{Department of Software, Sungkyunkwan University} \hfill \textit{Suwon, Korea}
    \begin{itemize}
        \item Assisted students with assignments and debugging sessions for Introduction to Programming.
        \item Held weekly office hours and prepared supplementary learning materials.
    \end{itemize}
\end{itemize}

%-----------SELECTED PROJECTS-----------
\section*{Selected Projects}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[]
    \textbf{Todo List Web Application} \hfill Sep. 2024 -- Dec. 2024 \\
    \textit{Team Project (3 members), Web Programming}
    \begin{itemize}
        \item Built a full-stack todo app with React frontend and Node.js/Express backend.
        \item Responsible for REST API design and database schema using MongoDB.
    \end{itemize}
    \item[]
    \textbf{Subway Delay Prediction Model} \hfill Mar. 2024 -- Jun. 2024 \\
    \textit{Individual Project, Machine Learning}
    \begin{itemize}
        \item Trained a Random Forest classifier on Seoul Metro open data to predict delays.
        \item Achieved 83\% accuracy; presented findings at the department poster session.
    \end{itemize}
\end{itemize}

%-----------HONORS & AWARDS-----------
\section*{Honors \& Awards}
\hrule
\vspace{4pt}
\begin{itemize}
    \item \textbf{Dean's List}, College of Software, Sungkyunkwan University \hfill 2023, 2024
    \item \textbf{Silver Prize}, SKKU Hackathon \hfill Nov. 2023
    \item \textbf{TOEIC} 860 / 990 \hfill Sep. 2023
    \item \textbf{Information Processing Engineer (Engineer Level)}, Human Resources Development Service of Korea \hfill May. 2024
\end{itemize}

%-----------EDUCATION-----------
\section*{Education}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[]
    \textbf{Sungkyunkwan University} \hfill Mar. 2022 -- Present \\
    \textit{B.E. in Software} \hfill \textit{Suwon, Korea}
    \begin{itemize}
        \item GPA: 3.7 / 4.5
        \item Relevant Courses: Data Structures, Algorithms, Operating Systems, Database Systems, \\
              Software Engineering, Open-Source Software Practice, Web Programming
    \end{itemize}
\end{itemize}

%-------------------------------------------
\end{document}